Foregrounds in Fourier Space for Redshifted 21~cm Observatories

### 2015-02-04 ms.tex
Bring figure3.eps under git version control
from 06e98c3:
============

(*) Bring figure3.eps under git version control as it was not done in
the previous commit
Add figure showing wide-field effects

from 28c0fe9:
============

(*) Bring figure3.eps under git version control

In ms.tex,

(*) Add figure showing wide-field effects under section "Wide-feild
measurements"

Figure ??? shows the wide--field delay power spectrum response of a uniformly illuminated sky with no spectral variation measured by antenna elements with a uniform power pattern across the sky. Notice the features arising due to the direction--dependent solid angle term and the steep rise in power towards the horizon limits. Wide--field effects are prevalent on all antenna spacings, including the longest ones used in this study.

>>>>

Figure~\ref{fig:usm} shows the wide--field delay power spectrum response of a uniformly illuminated sky with no spectral variation measured by antenna elements with a uniform power pattern across the sky. Notice the features arising due to the direction--dependent solid angle term and the steep rise in power towards the horizon limits. Wide--field effects are prevalent on all antenna spacings, including the longest ones used in this study.

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figure3.eps}
\caption{Delay power spectra of a uniform sky brightness distribution measured by antenna pairs with a uniform power pattern across the visible hemisphere. The non--zero response of the interferometer array to a uniform brightness distribution and the prominent {\it edge brightening} close to the horizon delay limits are due to wide--field effects. These effects are prevalent on all antenna spacings and are generic to all instruments used in wide--field measurements. \label{fig:usm}}
\end{figure}
